### 2015-11-03 CVPR16/Source/abstract.tex
latest version

\begin{abstract}
  We present a method to augment motion segmentation by representation of
  objects like cars with soft ellipsoids that not only present a probablistic
  alternative to bounding boxes but also inherently model occlusion. We compare
  our approach against state of the art motion segmentation methods.
\end{abstract}

>>>>

\begin{abstract}
We propose a model for representation of objects so that points can be
probabilistically  associated to the tracklets while accounting for occlusion.
We compare our approach against state of the art motion segmentation methods.
\end{abstract}

### 2015-11-03 CVPR16/Source/experiments.tex
latest version

%\begin{table}
%  \centering
%  \begin{tabular}{lccc}
%    \toprule
%    Algorithm & All & Unoccluded cars & Occluded cars \\
%    \midrule
%    bounding box only                         & $0.18\pm0.01$          & $\color{red}0.04\pm0.003$  & $0.41\pm0.04$\\
%    Using $\assocP{}$                         & $0.18\pm0.01$          & $0.05\pm0.003$           & $0.39\pm0.04$ \\
%    Using $P^{(ij)}_{\text{assoc by reproj}}$ & $0.18\pm0.01$          & $0.06\pm0.003$           & $0.39\pm0.04$\\
%    Using $P^{(ij)}_{\text{assoc}}$           & $\color{red}0.17\pm0.01$ & $0.05\pm0.003$           & $\color{red}0.38\pm0.04$\\
%    \bottomrule
%  \end{tabular}
%  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
%\end{table}
\begin{figure*}
\includegraphics[trim=1.0in 0.2in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{From top: (1)Association Experiment results on all points. %} \label{fig:assoc-results}
    (2) Association Experiment results on occluded points. %} \label{fig:assoc-occ-results}
    (3) Association Experiment results on dynamic points. %} \label{fig:assoc-dynamic-results}
    (4) Association Experiment results on dynamic  and occluded points. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. } \label{fig:assoc-occ-results}
\end{figure*}

>>>>

%\begin{table}
%  \centering
%  \begin{tabular}{lccc}
%    \toprule
%    Algorithm & All & Unoccluded cars & Occluded cars \\
%    \midrule
%    bounding box only                         & $0.18\pm0.01$          & $\color{red}0.04\pm0.003$  & $0.41\pm0.04$\\
%    Using $\assocP{}$                         & $0.18\pm0.01$          & $0.05\pm0.003$           & $0.39\pm0.04$ \\
%    Using $P^{(ij)}_{\text{assoc by reproj}}$ & $0.18\pm0.01$          & $0.06\pm0.003$           & $0.39\pm0.04$\\
%    Using $P^{(ij)}_{\text{assoc}}$           & $\color{red}0.17\pm0.01$ & $0.05\pm0.003$           & $\color{red}0.38\pm0.04$\\
%    \bottomrule
%  \end{tabular}
%  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
%\end{table}
\begin{figure*}
\includegraphics[trim=1.0in 0.2in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{From top: (1)Association Experiment results on dynamic and occluded tracks. %} \label{fig:assoc-results}
    (2) Association Experiment results on occluded points. %} \label{fig:assoc-occ-results}
    (3) Association Experiment results on dynamic points. %} \label{fig:assoc-dynamic-results}
    (4) Association Experiment results on all points. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. Occluded points are chosen because our method is especially helpful in occlusion cases while dynamic points are chosen for fair comparison against motion segmentation methods.} \label{fig:assoc-occ-results}
\end{figure*}

### 2015-11-03 CVPR16/Source/intro.tex
latest version

\section{Introduction}
The problem of segmenting points to objects often comes up in different
computer vision problems especially in multi-body 
reconstruction and localization. Given correspondence points on
consecutive frames, the problem becomes one of finding out which points belong
to which object following which one can use the consensus of segmented points
to reconstruct or localize the object more accurately. Without additional 
information this is very difficult problem as attempted by semantic segmentation 
and motion segmentation methods. However, in the problems like reconstruction and
localization on can use the hypothesis of the algorithm as the feedback. For

>>>>

\section{Introduction}
The problem of segmenting points to objects often comes up in different
computer vision problems especially in multi-body 
reconstruction and localization. Given correspondence points on
consecutive frames, the problem becomes one of finding out which points belong
to which object following which one can use the consensus of segmented points
to reconstruct or localize the object more accurately. Without additional 
information this is very difficult problem as attempted by semantic segmentation 
and motion segmentation methods. However, in the problems like reconstruction and
localization on can use the hypothesis of the algorithm as the feedback.
% What is the problem we are trying to solve, and why is it even important?

% What did we do
We propose a model for representation of objects in the scene so that points
can be probabilistically  associated to the tracklets while accounting for occlusion.
% Why is it novel
Although our proposed modeling is inspired by Milan et
al.\cite{Milan_etal_2014}, it is more detailed and more principled than their
work. Milan et al. used soft ellipses and sigmoids to model pedestrians and
their occlusion. We instead reason in 3D and use ellipsoids to model objects
and reason about occupancy of the space to model occlusion.
% Ok you proposed a model is it of any use
% How does it compare to state of art
We employ our model in the context of autonomous for problem of localization of
cars in the road scene. We show that associate points to objects more
accurately than other methods like bounding box based association, Brox and
Malik's\cite{Brox_Malik_2010} segmentation method and Robust Algebraic
Segmentation (RAS)\cite{Rao_etal_2010}.
